Tree-structured neural networks revisited

### 2016-03-04 writing/hard_stack_paper/paper.tex
Paper update.

Our model is based on a formalism adapted from transition-based parsing (\todo{What's a good classic citation for this?}).

@@

\paragraph{Equivalence with existing models}
If we add no additional features, this model computes the same function as a plain TreeRNN. However, we expect it to be substantially faster than conventional TreeRNN implementations. Unlike a TreeRNN, the Model 0 computation graph is essentially static across examples, so examples of varying structures and lengths can be batched together and run on the same graph in a single step. This simply requires ensuring that the graph is run for enough timesteps to finish all of the sentences. This involves some wasted computation, since the composition function will be run $2N-1$ times (with the output of composition at non-\reduce~steps discarded), rather than $N-1$ times in a TreeRNN. However, this loss can be dramatically offset by the gains of batching, which stem from the ability to exploit highly optimized CPU and GPU libraries for batched matrix multiiplication. \todo{Update.}

@@

This feature vector is then passed to a series of two (\todo{Update}) ReLU neural network layers, then passed into a linear transformation, and then finally passed to a softmax layer, which yields a distribution among the three labels.

@@

The tracking LSTM captures left context. \todo{Why?}

@@

We evaluate our model on the task of natural language inference (NLI), also known as recognizing textual entailment (RTE). NLI is a sentence pair classification task, in which a model reads two sentences (a premise and a hypothesis), and outputs a judgment of {\it entailment}, {\it contradiction}, or {\it neutral}, reflecting the relationship between the meanings of the two sentences, as here:

@@

In particular, we use the Stanford NLI corpus (SNLI, \citealt{snli:emnlp2015}). SNLI is a corpus of 570k human-labeled pairs of scene descriptions like the one above. We use the standard train--test split and ignore unlabeled examples, which leaves about 549k examples for training, 9,842 for development, and 9,824 for testing. SNLI labels are roughly balanced, with the most frequent label, {\it entailment}, making up 34.2\% of the test set.

@@

\begin{figure}
\vspace{14em}
\caption{\label{fig:induced-alignment}The alignment induced between two sentences by \todo{some model.}. Compare with a similar alignment presented by \protect\citealt{DBLP:journals/corr/WangJ15b}.}
\end{figure}

>>>>

Our model is based on a formalism adapted from transition-based parsing (\question{What's a good classic citation for this?}).

@@

@@

This feature vector is then passed to a series of two (\todo{Update w/ final number}) ReLU neural network layers, then passed into a linear transformation, and then finally passed to a softmax layer, which yields a distribution among the three labels.

@@

Lexical ambiguity is omnipresent in natural language. Most words have multiple senses or meanings, and it is generally necessary to use the context in which a word occurs to determine which of its senses or meanings is meant in a given sentence. Simpler sequence-based sentence encoding models like the standard LSTM RNN have an advantage here: when a sequence-based model first processes a word (first incorporates it into a partial sentence representation), the model has access to a state vector that summarizes all of the words to the left of the current word, and that state vector can serve as a crude but effective form of context to help with disambiguation. In contrast, when standard tree-structured models first process a word, they only have access to the constituent that the word is merging with, which is strictly less than the sequence model has access to, and is often just a single additional word.

In addition to our basic model, we additionally propose an extension that adds to the model (and exploits its sequential structure) by building in a parallel sequence-based model to track left context. This auxiliary model, called the tracking LSTM, maintains a low dimensional representation that is updated after every transition, thereby maintaining a representation of the left context at each time point. That representation is fed into the composition function as an additional input to allow for more efficient disambiguation. As long as the representations produced by the tracking LSTM are substantially smaller than those produced by the main composition function, the model is heavily biased towards computing sentence meaning compositionally according to the assigned tree structure, and is simply given the ability to do so with a better awareness of context.

@@

We evaluate our model on the task of natural language inference (NLI), also known as recognizing textual entailment (RTE). NLI is a sentence pair classification task, in which a model reads two sentences (a premise and a hypothesis), and outputs a judgment of {\it entailment}, {\it contradiction}, or {\it neutral}, reflecting the relationship between the meanings of the two sentences, as in this example from the Stanford NLI corpus (SNLI, \citealt{snli:emnlp2015}), which we use for training and evaluation:

@@

SNLI is a corpus of 570k human-labeled pairs of scene descriptions like the one above. We use the standard train--test split and ignore unlabeled examples, which leaves about 549k examples for training, 9,842 for development, and 9,824 for testing. SNLI labels are roughly balanced, with the most frequent label, {\it entailment}, making up 34.2\% of the test set.

@@

\begin{figure}
\vspace{14em}
\caption{\label{fig:induced-alignment}The alignment induced between two sentences by \result{one of our models.}. Compare with a similar alignment presented by \protect\citealt{DBLP:journals/corr/WangJ15b}.}
\end{figure}
